### 2018-12-11 Chapters/Chap3/Numerics.tex
commit

>>>>

\begin{align}
\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\bs{R}), \sin(\bs{Q}\bs{r}), 0 \right) \\
\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\bs{R} + \theta), \sin(\bs{Q}\bs{r} + \theta), 0 \right)
\end{align}

The $1, 2$ subindex stands for the sublattice. The $\hat{e}_z$ component vanishes in order to minimize the contribution of the pseudodipolar interaction. Then, the classical energy per spin is given by:

\begin{align}
\frac{E}{NS^2} &= -\frac{J_1}{2}\left( \cos(\theta) + \cos(\theta - Q_a - Q_b) + \cos(\theta - Q_b) \right) + \nonumber \\
&+ (J_2-\Gamma) \left( \cos(Q_a) + \cos(Q_b) + \cos(Q_a+Q_b) \right)+ \nonumber \\
&+D_2\left( \sin(Q_a) + \sin(Q_b) + \sin(Q_a+Q_b) \right)
\end{align}

The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space.
